A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-03-03 paper/methodology.tex
MCMC sketch

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
It has $3840^3$ dark matter particles of 
$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
The 2013 Planck cosmology is defined by the following parameters: $\Sigma_M = 0.307$, 
$\Sigma_B = 0.048$, $\Sigma_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
halos, to avoid incompleteness in the low mass end, halos with mass below 
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
cosmic variance can affect measurements, the original catalog is divided into 64 small 
cubic boxes, with a similar volume to the observations.

@@

The simplest relation we can have is a power law, two parametric function:
 \begin{equation}
    L_{\textrm{UV}} (M) = L_0 M^k
 \end{equation}
but it does not reproduce the two slopes in the UVLF.

A better model is a four parameter function. Each galaxy has a luminosity given
by:
  \begin{equation}
  L_{\textrm{UV}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.

Dust Extinction.

MCMC, maximum likelihood.

Python, Ipython Notebook, Scipy, Matplotlib, Numpy.

The galaxy UV luminosity can be directly related with SFR according to \citet{madau98}
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

>>>>

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
It has $3840^3$ dark matter particles of 
$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
The 2013 Planck cosmology is defined by the following parameters: $\Omega_M = 0.307$, 
$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
halos, to avoid incompleteness in the low mass end, halos with mass below 
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
cosmic variance can affect measurements, the original catalog is divided into 64 small 
cubic boxes, with a similar volume to the observations.

@@

\subsection{Fitting Model}

The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the four parameter model:
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.

%Dust Extinction
\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.

Observational data set to fit is selected.
A halo catalog of a cubic box of length 250 Mpc h-1 is selected.
Initial parameters are introduced.

An UV luminosity is given to each halo as function of his mass according to equation
 \ref{eqn:luminosity}.
Luminosity is converted to magnitude using:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}). \]

The luminosity function is constructed as an histogram of the magnitudes normalized by 
the volume of the catalog. Each observed luminosity function has a different bin range.

Once having the LF, we compare our LF against observed LF. Our likelihood estimator is 
the sum of the square difference over each bin, divided by the number of degrees of 
freedom. We worked on the logarithmic space of luminosities to have a good fitting on
six decades.

\[ \chi^2  = \sum_{i=o}^{n}\left( x_{i,obs} - x_{i,fit} \right)^2 \]

\[ \mathcal{L} \propto \exp \left( \frac{\chi ^2}{n} \right) \]

Then we have a small variation on the parameters, it gives us a new LF and a new 
likelihood estimator $\chi^2$.

We compare the new fitting versus the old fitting.

Some restrictions where imposed over two parameters to guarantee convergence in the 
MCMC method: $0 \leq \alpha \leq 1.8 $  and $\gamma \geq 0$.

%MCMC, maximum likelihood.

%Python, Ipython Notebook, Scipy, Matplotlib, Numpy. Astropy
Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

### 2015-03-03 paper/observations.tex
MCMC sketch

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bowens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

>>>>

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bowens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3} / \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
